### 2016-02-07 report/abstract.tex
Final report draft
Added paper draft.

\paragraph{Λέξεις Κλειδιά} Προσομοίωση ρευστών, τσουνάμι, \eng{SPH}, αλληλεπίδραση
τσουνάμι-α\-κτο\-γραμ\-μής, οπτικοποίηση δυνάμεων
% \end{minipage}
\cleardoublepage
% \begin{minipage}[b][0.49\textheight][t]{\textwidth}
\selectlanguage{english}
\section*{Abstract}
\paragraph{} The objective of this thesis was the accurate simulation of a tsunami hit on
a coastline. Emphasis was given to the conservation of momentum during the simulation, as
its distribution in space and time is the main factor of the wave's effects on the
coastline. Due to this, a hybrid simulation method was adopted, based on the SPH method
(Smoothed Particle Hydrodynamics), enriched with geometric constraints and rigid body
interactions. The implementation is the result of cooperation between the Bullet physics
engine and the custom SPH engine, which successively process the dynamic state of the
fluid at every timestep of the simulation. Furthermore, in order to achieve better
performance a custom data structure (LP grid) was developed for the optimization of
locality in data storage and minimization of access time. Simulation data is exported to
text files in VTK format to allow interactive processing and visualization with the aid of
specialized programs (like ParaView).
\paragraph{Keywords} Fluid simulation, tsunami, SPH, tsunami-coastline interaction,
force visualization

>>>>

\paragraph{Λέξεις Κλειδιά} Προσομοίωση ρευστών, τσουνάμι, \eng{SPH}, αλληλεπίδραση
τσουνάμι-α\-κτο\-γραμ\-μής, οπτικοποίηση δυνάμεων
% \end{minipage}
\clearpage
% \begin{minipage}[b][0.49\textheight][t]{\textwidth}
\selectlanguage{english}
\section*{Abstract}
\paragraph{} The objective of this thesis was the accurate simulation of a tsunami impact
upon a coastline. Emphasis was given to the conservation of momentum during the
simulation, as its distribution in space and time is the main factor of the wave's effects
on the coastline. Due to this, a hybrid simulation method was adopted, based on the SPH
method (Smoothed Particle Hydrodynamics), enriched with geometric constraints and rigid
body interactions. The implementation is the result of cooperation between the Bullet
physics engine and a custom SPH engine, which successively process the dynamic state of
the fluid at every timestep of the simulation. Furthermore, in order to achieve better
performance a custom data structure (LP grid) was developed for the optimization of
locality in data storage and minimization of access time. Simulation data is exported to
text files in VTK format to allow interactive processing and visualization with the aid of
specialized programs (like ParaView).
\paragraph{Keywords} Fluid simulation, tsunami, SPH, tsunami-coastline interaction,
force visualization
